\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}

\begin{document}
\author{Carlos Sebastian Madrigal Rodriguez}
\title{
    Impact of Vector Databases on Information Retrieval for Artificial Intelligence Agents Specialized in SDN API Documentation
    \\[0.3cm] \large A Comparative Study of FAISS, PGVector, and Neo4j in Retrieval-Augmented Generation Architectures.
}


% ==================== TITLE PAGE ====================
\begin{titlepage}
    \centering
    \vspace*{3cm}

    {\Huge\bfseries
    Impact of Vector Databases on Information Retrieval for Artificial Intelligence Agents Specialized in SDN API Documentation\par}

    \vspace{0.8cm}

    {\Large
    A Comparative Study of FAISS, PGVector, and Neo4j in Retrieval-Augmented Generation Architectures\par}

    \vspace{2cm}

    {\Large Carlos Sebastian Madrigal Rodriguez\par}

    \vfill

    {\large \today\par}
\end{titlepage}

\newpage % Forces the abstract onto the second page

% ==================== ABSTRACT ====================
\begin{abstract}

As modern networks become increasingly software-defined and API-driven, the ability of automation 
systems to understand and leverage their own capabilities has become a critical requirement. 
Network automation platforms often expose hundreds of APIs that enable configuration, monitoring, 
troubleshooting, and operational management tasks. However, these capabilities are typically documented 
in large and complex technical repositories, making it difficult for both automation systems and network 
engineers to efficiently discover and utilize the appropriate APIs for a given task. As a result, the 
full potential of network automation is often limited by the accessibility and usability of the available documentation.
\newline
\newline
Retrieval-Augmented Generation (RAG) architectures offer a promising approach for addressing this challenge 
by enabling agents to retrieve and reason over technical documentation in real time. 
Such agents could serve as an intelligent knowledge layer that allows automation systems to become aware of 
their available capabilities, dynamically identify suitable APIs, and support autonomous configuration, 
troubleshooting, and operational decision-making. This study investigates the impact of different vector database 
technologies on the effectiveness of this approach by comparing FAISS, PGVector, and Neo4j within a RAG-based 
architecture focused on SDN API documentation. The evaluation considers information retrieval accuracy, response 
quality, and retrieval latency to determine how the choice of vector database influences the performance of AI agents 
designed to enhance network automation and assist engineers in accessing complex technical information. 
Through this comparison, the research aims to identify the most suitable retrieval architecture for enabling intelligent, 
self-aware automation systems in Software-Defined Networking environments.

\end{abstract}

% Rest of your document goes here

\end{document}